### 2018-06-14 express2018/conclusions.tex
text

\section{Conclusions}
\label{s:concl}

@@

Further plan on the formalisation mainly includes: 1) the extension to
multi-variable equation/contractions. 2) the support of recursion operators in
CCS context and expressions.

The second author would like to thank many people from HOL community
for their help in the past two years: Michael Norrish, Thomas Tuerk, 
Ramana Kumar, Konrad Slind, and Jeremy Dawson. The second half of this
paper was written in memory of  Mike J. Gordon.

>>>>

\section{Conclusions and future work}
\label{s:concl}

@@

Further plan on the formalisation mainly includes: 1) the extension to
multi-variable equation/contractions. 2) the support of recursion operators in
CCS context and expressions.
\subsection*{Acknowledgements}

We would like to thank many people from the HOL community
for their help in the past two years, in particular: 
Michael Norrish, Thomas Tuerk, 
Ramana Kumar, Konrad Slind, and Jeremy Dawson. 
% The second half of this
% paper was written in memory of  Mike J. Gordon.
